Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-10 body.tex
Put the condition in pseudocode like equations

\begin{verbatim}
function gravity(P, model):
  result = 0
  for each tesseroid in model:
    d = distance from P to the top of tesseroid
    if d < r*L_lon:
      divide_lon = true
    if d < r*L_lat:
      divide_lat = true
    if d < r*L_r:
      divide_r = true
    if divide_lon or divide_lat or divide_r:
      newmodel = (divide tesseroid in the
                  required dimensions)
      result = result + gravity(P, newmodel)
    else
      result = result + effect of tesseroid
  return result
\end{verbatim}

>>>>

\begin{verbatim}
function gravity(P, model):
  result = 0
  for each tesseroid in model:
    d = distance from P to the top of tesseroid
    if d/L_lon < r:
      divide_lon = true
    if d/L_lat < r:
      divide_lat = true
    if d/L_r < r:
      divide_r = true
    if divide_lon or divide_lat or divide_r:
      newmodel = (divide tesseroid in the
                  required dimensions)
      result = result + gravity(P, newmodel)
    else
      result = result + effect of tesseroid
  return result
\end{verbatim}
